LogChunks: A Data Set for Build Log Analysis

### 2020-01-14 msr-paper/paper.tex
Edit abstract

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Build failures are common in continuous integration (CI), but identifying the root cause of a failure is difficult.
To stimulate research in this area, we present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
For each build log we manually labeled the log part (chunk) describing why the build failed.
We validated the data set by surveying the developers of the projects which produced the builds.
The width and depth of the \emph{LogChunks} data set makes it an ideal basis to benchmark build log analysis techniques.
Various tools have been proposed to boil down verbose build logs to the specific lines valuable to the developer.
Benchmarking different techniques will advance the research area of build log analysis and ultimately increase our understanding of CI build failures.
\end{abstract}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Build logs are the textual by-products that a software build processes
creates, often as part of a Continuous Integration (CI)
pipeline. Build logs are a paramount source of information for
developers when debugging into and understanding a build
failures. Recently, attempts to partly automate this time-consuming,
purely manual activity have come up, such as rule- or
Information-Retrieval-based techniques.

While still in their infancy, we believe that having a common dataset
to be able to fairly compare different build log analysis techniques
will advance the research area and ultimately increase our
understanding of CI build failures. In this paper, we present
\emph{LogChunks}, a collection of 797 fully annotated Travis CI build
logs from 80 GitHub repositories in 29 programming languages. For each
build log, LogChunks contains a manually labeled log part (chunk)
describing why the build failed. We externally validated the data set
with the developer who caused the original build failure.

In our opinion, the width and depth of the \emph{LogChunks} data set
makes it an ideal benchmark for automated build log analysis
techniques.
\end{abstract}
